\documentclass[12pt,letterpaper]{article}


\usepackage{wrapfig}                % For text-wrapping figures
\usepackage{graphicx}        % For making figures (.png, .jpg, and .pdf supported)
\usepackage{color}        % For a variety of text recoloring options
\usepackage{amsmath}        % For non-italic \text{} in subscripts--included if using mhchem
\usepackage{mathtools}        % For declaring paired delimiters
\usepackage{multirow}        % For tables with rows taller than 1 line
\usepackage[version=3]{mhchem}        % For typesetting chemical formulae
\usepackage{setspace}        % For configuring line spacing
%\usepackage[ampersand]{easylist}        % For making lists easily
\usepackage{pifont}        % For using wingdings (check and X, specifically)
\usepackage[top=1in, left=1.25in, bottom=1in, right=1.25in]{geometry}        % Sets margins
\usepackage{hyperref}
\usepackage{xfrac}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\newcommand{\ch}{{\ding{51}}}        % Insert a check mark by typing {\ch}
\newcommand{\X}{{\ding{55}}}        % Insert an X mark by typing {\X}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}        % For absolute value signs


\title{ASTR 150: The Planets\\ \vspace{0.25cm} \large{TA syllabus}}
\author{Marshall J. Styczinski}
\date{Winter 2017}        

\begin{document}
\maketitle
\onehalfspacing
\thispagestyle{empty}

\section{TA info}
	\begin{tabbing}
		\textbf{Section AE meets:}		\= MW 12:30p--1:30p\\
		\textbf{Section AJ meets:}	\> MW 11:30a--12:30p\\[\baselineskip]
		\textbf{Office hours:}	\> Tue 11:30a--12:30p\\
			\> Wed 1:30p--2:30p\\
		\textbf{Office:}\> \href{http://students.washington.edu/mjstyczi/images/PAT_map.png}{Physics/Astronomy Tower, room C221}\\	
		\textbf{Email:}\> mjstyczi@uw.edu\\
		\textbf{Website:}\> \url{http://students.washington.edu/mjstyczi/}

	\end{tabbing}

	I am very responsive to email. Please send me emails from your @uw.edu address to ensure delivery.
	
	If you are unable to attend my office hours, please send me an email to arrange another time to meet.
	

\section{Expectations}
	Discussion section is your chance to get practice working with astronomy ideas. You are expected to arrive ready to openly discuss your reasoning with your group and with me, your TA. I am here to help \textit{you} learn, and you will learn much more if you participate in discussions and activities. Raise your hand at any time during class to ask a question. You are also welcome to send questions via email.
	
\section{Assignment grading}
	Exercises assigned in class are handed in to be graded. Each module is due at the start of class 1 week after it is assigned in class. Questions will typically be graded 50\% for correct answer, 50\% for showing your work or explaining your reasoning. No late work will be accepted.

	{\ch} indicates a correct or approved response;
	
	{\X} indicates an incorrect or flawed response.
	
	The work you submit must be your own. No credit will be awarded for copying on reading assignments. Blatant copying on worksheets will result in the awarded points being divided among the number of identical responses. For example, if 4 students hand in identical assignments, each student will earn $\sfrac{1}{4}$ of the point value for the work submitted. Repeat offenders will be reported for academic misconduct.

\section{Participation credit}
	5\% of your overall course grade is devoted to participation in discussion section. Your participation grade is determined using the following criteria:\\

	\begin{tabular}{ | c | l | }
		\hline
		80\%	&	Attendance and collaboration with group\\
		\hline
		20\%	&	Leading discussion after in-class presentation\\
		\hline
	\end{tabular}\\
	
Simply showing up to class on time and working with your group will earn 80\% of your participation credit. If you are unable to attend class on a particular day, email the TA of another section \textbf{at least 24 hours in advance} requesting permission to attend, and cc me at \mbox{mjstyczi@uw.edu}. All assignments should still be handed in to me in discussion or lecture. Late work will not be accepted, so hand your work in early if you will be missing class. You may only attend another section one time for participation credit.

Everyone must also give a 2-3 minute presentation on a weekly reading assignment. At the end of your presentation, you'll lead a class discussion. Start your class discussion with a question you submitted with your reading assignment, one you wondered about from your reading. 20\% of your participation grade will be based on leading a few minutes of class discussion following your presentation.

Volunteer for a particular date at the link that will be posted here soon.

\thispagestyle{empty}
\end{document}